Paper Figure Generation

### 2022-06-24 R/PaperFigureGeneration.rmd
Finished first draft of figures

```{r figure_3A}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
```
```{r figure_3B}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_3C}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
                        expansionOffset = 10, minReadLength = 21, maxReadLength = 27)

@@

yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMismatchDataAllRepsFiltered)) {
  yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

@@

yeastCPDMMFreqZScoresAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMMFreqZScoresAllRepsFiltered)) {
  yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(yeastCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

@@

```{r figure_5A}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
```
```{r figure_5B}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)

@@

plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(24:30))

plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:25))

@@

```{r figure_6A}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_6B}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
```
```{r figure_6C}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

@@

```{r figure_7B}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD", Timepoint = "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(x = Mismatch_Type, y = Tandem_Mismatches_Count)) +
      geom_bar(aes(fill = Search_Method), stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      blankBackground + defaultTextScaling
  )
```

@@

NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "GG>AA",
    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
  ))
}

```{r figure_8}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD 1h All Reps CC>TT Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)

plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD 1h All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
# 
# plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
```

@@

```{r read_figure_S3_data}
arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
    timepoint = names(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

@@

```{r figure_S3}
plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$ZT2,
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 15, maxReadLength = 25)

>>>>

```{r figure_3A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
```
```{r figure_3B, fig.width = 6, fig.height = 5}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_3C, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
                        expansionOffset = 10, minReadLength = 21, maxReadLength = 27)

@@

yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMismatchDataAllRepsFiltered)) {
  yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

@@

yeastCPDMMFreqZScoresAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMMFreqZScoresAllRepsFiltered)) {
  yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(yeastCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

@@

```{r figure_5A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
```
```{r figure_5B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)

@@

plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(24:30))

plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:25))

@@

```{r figure_6A, fig.width = 6, fig.height = 5}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_6B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
```
```{r figure_6C, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

@@

```{r figure_7B, fig.width = 8, fig.height = 5}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD" & Timepoint == "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25) +
      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1")
  )
```

@@

NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

NHF1CPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)) {
  NHF1CPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
  ))
}

arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)) {
  arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
  ))
}

yeastCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(yeastCPDCCToTTGroupedStatsAllRepsFiltered)) {
  yeastCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(yeastCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
  ))
}
```

```{r figure_8A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
```
```{r figure_8B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
```
```{r figure_8C}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

### All timepoints together ###
# plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
#                          NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
#                          xAxisBreaks = c(22:30))
```
```{r figure_8D}
### Just the 1h timepoint ###
plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
                         xAxisBreaks = c(24:30))

### All timepoints together ###
# plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
#                          arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
#                          xAxisBreaks = c(24:30))
```
```{r figure_8E}
### Just the 1h timepoint ###
plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
                         xAxisBreaks = c(22:25))

### All timepoints together ###
# plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
#                          yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
#                          xAxisBreaks = c(22:25))
```

@@

```{r figure_S3, fig.width = 9, fig.height = 5}
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered,
                               title = "NHF1 CPD ALL Reps TGG-Filtered 5' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```

```{r read_figure_S4_data}
arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
    timepoint = names(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

@@

```{r figure_S4, fig.width = 9, fig.height = 5}
plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                        title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19)
```
